### 2012-03-09 doc/theses/mikula/analysis_of_xquery.tex
Master thesis: In progress.

\texttt{lt} is a representant of so called \emph{value comparison operators} \todo{referencia na def} which operate two sequences of zero or one item. If an operand of a value comparison operator is a sequence of more than one item, then a \emph{type error} \todo{referencia na def} is raised.

>>>>

\texttt{lt} is a representant of so called \emph{value comparison operators} (\texttt{eq}, \texttt{ne}, \texttt{lt}, \texttt{le}, \texttt{gt}, \texttt{ge}, see \cite{w3c_xquery}) which operate two sequences of zero or one item. If an operand of a value comparison operator is a sequence of more than one item, then a \emph{type error} (see \cite{w3c_xquery}) is raised.
